---
title: "R Notebook"
output: html_notebook
---

## Desired functions:

### Reading in (and cleaning) data:
* `load_BMG(file)`
* `load_tecan(file)`

### Fitting curves:
* `grofitr(data, time, options)`
    * Should call `grofit()` directly
    * Should output a data.frame/tibble (if only one plate) or list of data.frames/tibbles (if multiple plates) of estimated parameters and stats

### Merging metadata (Media, genotype, etc)
* Simple use of `left_join()` or other

### Plotting data
* Plot 96 wells at a time, for quick-checking
* Plot curves with estimated parameters
    * How to accurately represent uncertainty in multiple parameters when plotting estimated slope line?


### Other
* How to handle evaporation?
    * Manual inspection, re-do with time cutoff (specific per well)
    * Automatic detection of evaporation
    * Always do a completely blank plate
* Goal work flow:
    * Single plate
    ```
    "file.csv" %>% 
    load_BMG() %T% plot_plates() %>% 
    grofitr() %>% 
    merge_meta()
    ```
    * Multiple plates
    ```
    c("file1.csv", "file2.csv", "file3.csv") %>% 
    load_BMG() %T% plot_plates() %>% 
    grofitr() %>% 
    merge_meta() %>%
    ```

* Take file name(s) of data, read it in, and convert it to grofit-friendly 'data' df and 'time' matrix

```{r setup}
library(stringr)
library(dplyr)
library(dplyr)
library(magrittr)
library(readr)
```

```{r time_to_dbl}
time_to_dbl <- function(t) {
  t %>%
    stringr::str_replace_all("(\\d+) h( (\\d+) min)?", "\\1.0\\3") %>%
    stringr::str_split(string = ., pattern = "\\.") %>%
    sapply(FUN = function(x) {
      x %>% as.numeric() %>%
        magrittr::extract(2) %>%
        magrittr::divide_by(60) %>%
        magrittr::add(as.numeric(x[1]))
    })
}

time_to_dbl(c("43 h", "234 h 2 min", "0 h 1 min"))
```

```{r get_barcode}
file <- "~/1_Research/DATA/phenotyping/plate reader/2017-08-21-Stacker8/TRno1886.CSV"

get_barcode_BMG <- function(file, trim = FALSE) {
  if (trim == TRUE) {
    file %>% readLines() %>% 
      grep("ID1: ", ., value = T) %>% 
      str_extract("(?<=ID1: ).*(?= \\d{1,2}/\\d{1,2}/\\d{2,4})") %>%
      substr(regexpr("[^0]", .), nchar(.))
  } else if (trim == FALSE) {
    file %>% readLines() %>% 
      grep("ID1: ", ., value = T) %>% 
      str_extract("(?<=ID1: ).*(?= \\d{1,2}/\\d{1,2}/\\d{2,4})")
  }
}

get_barcode_BMG(file, trim = TRUE)
get_barcode_BMG(file, trim = F)
```

```{r load_BMG}
# Add option to extract barcode? Would store in "plate" column. 

load_BMG <- function(file, get.barcode = FALSE) {
  x <- file %>%
    readLines() %>%
    grepl("Well Row", .) %>%
    which() %>%
    subtract(1) %>%
    read_csv(file, skip = .)# %>%
  x <- x %>% rename_at(vars(-c(1:3)),
                  funs(x %>% slice(1) %>% select(-c(1:3)))) %>%
    dplyr::slice(-1) %>%
    tidyr::gather(time, OD, -`Well Row`, -`Well Col`, -Content) %>%
    dplyr::mutate(time = time_to_dbl(time), OD = as.numeric(OD))
  if (get.barcode == TRUE) {
    x <-  dplyr::mutate(plate = get_barcode_BMG(file))
  } else {
    x <-  dplyr::mutate(plate = basename(file) %>%
                        strsplit("\\.") %>% `[[`(1) %>% `[`(1))
  }
}

R73G <- load_BMG("~/1_Research/DATA/phenotyping/plate reader/2017-07-19-Stacker6/TRno1806.CSV")
```

```{r grofitr}
#' @import grofit
#' @import magrittr

# TODO: Add option to truncate data at certain time
# TODO: Add options for setting grofit.control() options
grofitr <- function(plate, control = grofit.control(...)) {
  timepoints <- plate %>% select(time) %>% unique() %>% unlist()
  n <- length(timepoints)
  times <- timepoints %>% rep(96) %>% matrix(c(n, 96)) %>% t()
  
  plate <- plate %>% 
    dplyr::mutate(OD = as.numeric(OD)) %>% 
    tidyr::spread(time, OD) %>%
    dplyr::select(-Content) %>%
    dplyr::select(3,1,2,4:length(.))# %>%
  
  grofit::grofit(times, plate, ec50 = F, control = control) %$% gcFit %$% gcTable
}

R73G_results <- "~/1_Research/DATA/phenotyping/plate reader/2017-07-19-Stacker6/TRno1806.CSV" %>% 
  load_BMG() %>% 
  grofitr(control = grofit.control(interactive = FALSE, 
                                   suppress.messages = TRUE, 
                                   nboot.gc = 100)
          )
```

```{r merge_meta}
merge_meta <- function(data)
```

```{r plot_plate}
plot_plates <- function(data){
  ggplot(data, aes(x = time, y = OD)) +
    geom_point(size = 0.2) + 
    geom_line() +
    facet_grid(`Well Row` ~ `Well Col`, switch = "y") +
    scale_y_continuous(position = "right") +
    theme_bw() +
    theme(panel.grid = element_blank())
  }
```
